Plug-and-play dual-tree algorithm runtime analysis

### 2015-10-23 bounds-files/general-runtime-bound.tex
Update explanation.

Because we have shown that the condition holds for the initial reference set and
for any reference set produced by a reference recursion, we have shown that the
statement of the lemma is true.
\end{proof}

>>>>

Because we have shown that the condition holds for the initial reference set and
for any reference set produced by a reference recursion, we have shown that the
statement of the lemma is true.

Note that in this proof, we have considered the child reference set $R_{r - 1}$,
not the original reference set $R$, and shown that with respect to $s_r^{\max}$
as defined by $R$ (not $R_{r - 1}$), all nodes are separated by $2^{s_r^{\max} -
1}$.  Then, in the frame of the next recursion where $R \gets R_{r - 1}$, the
lemma will hold, as $s_r^{\max}$ will then be the maximum scale present in $R$.
\end{proof}
